Data Descriptive: Corresponding author journal publishing activities 2014 - 2018

### 2019-10-05 analysis/paper.Rmd
some minor fixes

```{r}
tt_oa <- my_df %>%
  mutate(publisher_group = ifelse(publisher %in% tt_all$publisher_group, publisher, "Other")) %>%
  group_by(publisher_group, oa_journal) %>%
  summarise(n = sum(articles)) %>%
  mutate(oa_journal = ifelse(oa_journal == TRUE, "in Fully Open Access Journals", "in Subscription Journals")) %>%
  ungroup() %>%
  group_by(oa_journal) %>%
  mutate(prop = n / sum(n))
plot_df <- tt_all %>%
  mutate(oa_journal = "Overall Article Volume") %>%
  bind_rows(tt_oa) %>%
  group_by(oa_journal) %>%
  mutate(label = format(sum(n), big.mark   = ",")) %>%
  mutate(label = paste0(oa_journal, " (", label, " Articles)")) %>%
  ungroup() %>%
  mutate(publisher_group = factor(publisher_group, levels = levels(tt_all$publisher_group)))
london_palette <-
  c(
    "#6da7de",
    "#9e0059",
    "#dee000",
    "#d82222",
    "#5ea15d",
    "#943fa6",
    "#63c5b5",
    "#ff38ba",
    "#eb861e",
    "#ee266d"
  )
p_bar <-
  ggplot(plot_df, aes(x = "", y = prop, fill = publisher_group)) +
  geom_bar(width = 1,
           stat = "identity",
           position = position_stack(reverse = FALSE)) +
  facet_wrap( ~ label, ncol = 1) +
  coord_flip() +
  geom_text(aes(label = paste0(round(prop, 2) * 100, "")), position = position_stack(vjust = .5)) +
  scale_fill_manual(
    "",
    values = c("grey80", rev(london_palette[1:10])),
    guide = guide_legend(reverse = TRUE,  ncol = 4)
  ) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1),
                     labels = scales::percent_format(accuracy = 5L)) +
  labs(
    title = "Global Publisher Market Shares 2014 - 2018",
    x = "",
    y = "",
    subtitle = "Original Articles and Reviews indexed in the Web of Science\n\n",
    caption = "Data Sources:  Web of Science in-house database Competence Centre for Bibliometrics for German Science. 
    Publisher names were disambiguated using Crossref metadata. OA status obtained from the Bielefeld GOLD OA list.
    Funding: Federal Ministry of Education and Research of Germany (BMBF), Project OAUNI (01PU17023A)"
  ) +
  #  scale_y_continuous(breaks = seq(0,1, by =0.1), labels = scales::percent_format(accuracy = 5L)) +
  theme_minimal(base_family = "Roboto", base_size = 16) +
  theme(plot.margin = margin(30, 30, 30, 30)) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(legend.position = "bottom",
        legend.justification = "center")
dir.create("figure")
ggsave(
  filename = "figure/global_publisher_share.png",
  plot = p_bar,
  width = 14,
  height = 9,
  dpi = 300
)
```

>>>>

```{r}
tt_oa <- my_df %>%
  mutate(publisher_group = ifelse(publisher %in% tt_all$publisher_group, publisher, "Other")) %>%
  group_by(publisher_group, oa_journal) %>%
  summarise(n = sum(articles)) %>%
  mutate(oa_journal = ifelse(oa_journal == TRUE, "Fully Open Access", "Subscription")) %>%
  ungroup() %>%
  group_by(oa_journal) %>%
  mutate(prop = n / sum(n))
plot_df <- tt_all %>%
  mutate(oa_journal = "All Journals") %>%
  bind_rows(tt_oa) %>%
  group_by(oa_journal) %>%
  mutate(label = format(sum(n), big.mark   = ",")) %>%
  mutate(label = paste0(oa_journal, " (", label, " Articles)")) %>%
  ungroup() %>%
  mutate(publisher_group = factor(publisher_group, levels = levels(tt_all$publisher_group)))
london_palette <-
  c(
    "#6da7de",
    "#9e0059",
    "#dee000",
    "#d82222",
    "#5ea15d",
    "#943fa6",
    "#63c5b5",
    "#ff38ba",
    "#eb861e",
    "#ee266d"
  )
p_bar <-
  ggplot(plot_df, aes(x = "", y = prop, fill = publisher_group)) +
  geom_bar(width = 1,
           stat = "identity",
           position = position_stack(reverse = FALSE)) +
  facet_wrap( ~ label, ncol = 1) +
  coord_flip() +
  geom_text(aes(label = paste0(round(prop, 2) * 100, "")), position = position_stack(vjust = .5)) +
  scale_fill_manual(
    "",
    values = c("grey80", rev(london_palette[1:10])),
    guide = guide_legend(reverse = TRUE,  ncol = 4)
  ) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1),
                     labels = scales::percent_format(accuracy = 5L)) +
  labs(
    title = "Global Publisher Market Shares 2014 - 2018",
    x = "",
    y = "",
    subtitle = "Original Articles and Reviews indexed in the Web of Science\n\n",
    caption = "Data Sources:  Web of Science in-house database Competence Centre for Bibliometrics for German Science. 
    Publisher names were disambiguated using Crossref metadata. OA status obtained from the Bielefeld GOLD OA list.
    Funding: Federal Ministry of Education and Research of Germany (BMBF), Project OAUNI (01PU17023A)"
  ) +
  #  scale_y_continuous(breaks = seq(0,1, by =0.1), labels = scales::percent_format(accuracy = 5L)) +
  theme_minimal(base_family = "Roboto", base_size = 16) +
  theme(plot.margin = margin(30, 30, 30, 30)) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(legend.position = "bottom",
        legend.justification = "center")
dir.create("figure")
ggsave(
  filename = "figure/global_publisher_share.png",
  plot = p_bar,
  width = 14,
  height = 9,
  dpi = 300
)
```
